Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

This subsection will explain how to find the $k$-tuples of Type 1. Let us represent the set of such tuples as $\J_1(R_1, ..., R_{k-2}, H, V)$ and define its ``projection'' onto $(R_1, ..., R_{k-2})$ as
\myeqn{
    && \Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V)) \nn \\
    &=& \{(r_1, ..., r_{k-2}) \mid (r_1, ..., r_{k-2}, h, v) \in \J_1(R_1, ..., R_{k-2}, H, V)
    \}. \nn
}
We will compute $\J_1(R_1, ..., R_{k-2}, H, V)$ in two steps:
\myitems{
    \item {{\bf Step 1:}} Compute $\Pi_{1:k-2}(\J_1(R_1, ..., R_{k-2}, H, V))$;
    \item {{\bf Step 2:}} Generate $\J_1(R_1, ..., R_{k-2}, H, V)$ from the result of Step 1.
}

\noindent {\bf Step 1.} We will accomplish this step by solving an instance of $(k-2)$-SJ. To construct the instance, for each rectangle $r_1 \in R_1$, we compute four segments:
\myitems{
    \item $h_1$ (resp., $h_2$): the lowest (resp., highest) segment --- i.e., with the smallest (resp., largest) y-coordinate --- among all the segments in $H$ that cross $r$;

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle defined by the above four segments in the way shown in Figure~\ref{fig:hv:type1}(a) ($r_1'$ is the shaded area). Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}}. \nn
}
Computing the corresponding ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\mathscr{A}$. By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time.

>>>>

As before, let $R_1, ..., R_{k-2}, H$, and $V$ be the input sets of the H-V $k$-SJ problem. Denote by $\J_1$ the set of type-1 result tuples defined in Section~\ref{sec:hv}. In this section, we aim to compute a set $\J^*$ satisfying
\myeqn{
    \J_1
    \subseteq
    \J^*
    \subseteq
    \J(R_1, ..., R_{k-2}, H, V) \label{eqn:hv:type1:S}
}
where $\J(R_1, ..., R_{k-2}, H, V)$, let us recall, is the join result of the (whole) H-V $k$-SJ. From $\J^*$, we will report only those $k$-tuples belonging to $\J_1$ and ignore the rest.

\extraspacing {\bf The Sets $\bm{R_1', R_2', ..., R'_{k-2}}$.} For each rectangle $r_1 \in R_1$, we compute four segments:
\myitems{
    \item $h_1$ (resp., $h_2$): the lowest (resp., highest) segment --- i.e., with the smallest (resp., largest) y-coordinate --- among all the segments in $H$ that cross $r$;

    \item $v_1$ (resp., $v_2$): the leftmost (resp., rightmost) segment --- i.e., with the smallest (resp., largest) x-coordinate --- among all the segments in $V$ that cross $r$.
}
Define $r_1'$ as the rectangle bounded by the above four segments as shown in Figure~\ref{fig:hv:type1}(a) ($r_1'$ is the shaded area). Note that $r_1'$ exists if and only if $r_1$ is crossed by at least one horizontal segment in $H$ and by at least one vertical segment in $V$. Moreover, it is possible for $h_1$ and $h_2$ to be the same segment; same for $v_1$ and $v_2$. Define
\myeqn{
    R_1' &=& \set{r_1' \mid r_1 \in R_1 \text{ and its $r_1'$ defined as above exists}} \nn
}
which we refer to as the {\em trimmed} version of $R_1$. Computing the ``segment $h_1$'' for each $r_1 \in R_1$ is an instance of Problem $\mathscr{D}$ (the first-crossing version). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r_1 \in R_1$. It thus follows from Section~\ref{sec:bricks} that $R_1'$ can be produced in $O(n \log n)$ time.
